---
title: "p8105_hw1_Ec3342"
author: "Ekta Chaudhary"
date: "19/09/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1
#Here's the first **code chunk** that creates a data frame called first_df comprised of a random sample named norm_samp of size 8 from a standard normal distribution, a logical vector named vec_log indicating whether elements of the sample are greater than 0, a character vector named vec_char of length 8 and a factor vector named vec_factor of length 8, with 3 different factor levels- Here the three levels are 1,2 and 3. After creating the data frame, I tried taking the mean of each variable in the data frame. mean_norm gives the mean of the random sample- norm_samp; mean_log gives us the mean of the logical vector- vec_log. When I tried taking the mean of the character vector- vec_char and the factor vector- vec_factor, I got an error saying the argument is not numeric or logical: returning N/A. Next I applied the as.numeric function to the logical, character, and factor variables. When I applied the as.numeric function, the logical vector, character vector and the factor vector gets converted to numeric. When I tried taking the mean after this conversion, I no longer got the error. Applying as.numeric function allows us to take the mean of each variable in our dataframe.

```{r first_chunk}

library(tidyverse)

first_df = tibble(
  norm_samp = rnorm(8),
  vec_log = norm_samp > 0,
  vec_char = c("1","2","3","4","5","6","7","8"),
  vec_factor = factor(c("1","2","3","1","2","3","1","2")),
)
mean_norm = mean(pull(first_df,norm_samp)) 

mean_log = mean(pull(first_df,vec_log))

mean_char = mean(pull(first_df,vec_char))

mean_fac = mean(pull(first_df,vec_factor))

mean(as.numeric(first_df[["vec_log"]]))
mean(as.numeric(first_df[["vec_char"]]))
mean(as.numeric(first_df[["vec_factor"]]))

```
