---
title: "p8105_hw1_Ec3342"
author: "Ekta Chaudhary"
date: "19/09/2019"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Question 1

## Creating a Data Frame: 
#Here's the first **code chunk** that creates a data frame called first_df comprised of a random sample named norm_samp of size 8 from a _standard normal distribution_, a logical vector named vec_log indicating whether elements of the sample are greater than 0, a character vector named vec_char of length 8 and a factor vector named vec_factor of length 8, with 3 different factor levels.

```{r first_chunk}

library(tidyverse)

first_df = tibble(
  norm_samp = rnorm(8),
  vec_log = norm_samp > 0,
  vec_char = c("1","2","3","4","5","6","7","8"),
  vec_factor = factor(c("1","2","3","1","2","3","1","2")),
)
mean(pull(first_df,norm_samp)) 
mean(pull(first_df,vec_log))
mean(pull(first_df,vec_char))
mean(pull(first_df,vec_factor))

```
#After creating the data frame, I tried taking the mean of each variable in the data frame. I got the mean of the random sample (norm_samp) and the logical vector (vec_log).However, when I tried taking the mean of the character vector (vec_char) and the factor vector (vec_factor), I got an error saying the argument is not numeric or logical:returning N/A.

#Now writing a **code chunk** to apply the **as.numeric** function to the logical, character, and factor variables. Hiding the output by giving **eval = FALSE** in the code chunk. After applying the as.numeric function, the logical vector, character vector and the factor vector gets converted to numeric because as.numeric will return the numeric codes that correspond to the logical vector, character vector and factor vector. If we try taking the mean after this conversion, we no longer get an error. Therefore, applying as.numeric function allows us to take the mean of each variable in our dataframe, first_df.

``````{r conversion_chunk, eval = FALSE}

as.numeric(pull(first_df,vec_log))
as.numeric(pull(first_df,vec_char))
as.numeric(pull(first_df,vec_factor))

mean(as.numeric(pull(first_df,vec_log)))
mean(as.numeric(pull(first_df,vec_char)))
mean(as.numeric(pull(first_df,vec_factor)))

```
## Second code chunk
#Here's the second **code chunk** that is Converting the logical vector (vec_log) to numeric using the **as.numeric** function and then multiplying the result with the random sample(norm_samp).  Converting the logical vector (vec_log) to factor vector using the **as.factor** function and then trying to multiply the result with the random sample(norm_samp). On doing so, I got an error here saying '*' is not meaningful for factors. Converting the logical vector to a factor vector using as.factor and then converted the result to numeric using as.numeric; followed by multiplying the result with the random sample.On doing so,I didn't get any error because I first converted the factor vector into numeric and then multiplied that with the random sample.

```{r second_chunk}

as.numeric(pull(first_df,vec_log))*(pull(first_df,norm_samp))
as.factor(pull(first_df,vec_log))*(pull(first_df,norm_samp))
as.numeric(as.factor(pull(first_df,vec_log)))*(pull(first_df,norm_samp))

```

# Question 2 
## Creating a data frame 
#Creating a data frame named second_df comprised of: x which is a random sample of size 500 from a standard Normal distribution, y which is a random sample of size 500 from a standard Normal distribution, A logical vector (vec_log2) indicating whether x + y > 1, a numeric vector (vec_num), created by coercing the above logical vector and a factor vector(vec_fac) created by coercing the above logical vector

```{r question 2}

library(tidyverse)

second_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  vec_log2 = x + y > 1,
vec_num = as.numeric(vec_log2),
vec_fac = as.factor(vec_log2),
)

```
## Description of the dataframe

* The size of the dataframe is `r nrow(second_df)` and the number of columns are `r ncol(second_df)`
* The mean of x is `r mean(pull(second_df,x))` 
* The median of x is `r median(pull(second_df,x))` 
* The standard deviation of x is `r sd(pull(second_df,x))`
* The proportion of cases for which x + y > 1 is 
`r sum(pull(second_df,vec_log2),na.rm = TRUE)/nrow(second_df)`

## Scatterplot 
#Creating a scatterplot (plot_1) of y vs x that color points using the logical variable, a second scatterplot (plot_2) that color points using the numeric variables, and a third scatterplot that color plots using the factor variables.Exporting the first scatterplot (plot_1) to my project directory using ggsave.

```{r scatterplot}

plot_1 = ggplot(second_df, aes(x = x, y = y, color = vec_log2)) + geom_point() 
plot_1
plot_2 = ggplot(second_df, aes(x = x, y = y, color = vec_num)) + geom_point() 
plot_2
plot_3 = ggplot(second_df, aes(x = x, y = y, color = vec_fac)) + geom_point() 
plot_3
ggsave("plot_1.pdf", height = 4, width = 6)

```




